---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css echo=FALSE}
body {
  font-size: 12pt;
  font-family: "Calibri";
  color: #000000;
  background-color: #D2E4EF;
}
h2 {
  font-size: 25px;
  color: #083854;
  border-bottom: 2px solid #333;
  padding-bottom: 5px;
}

```

## Exploring Engagement, Ads, and Content Trends on TikTok
From 15-second clips to sponsored posts: Measuring what surfaces on the FYP
```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTDYE3S0F4zhOhNt6YOB2c0fUG2vQ0ziwd4CWJSvPtnLxaMIw1UoO4BawcK3U347uUIOt6kaDOMeNxZ/pub?output=csv")

# Creating new data frame & Re-naming variables
latest_data <- logged_data %>%
  rename(video_duration = 2,
         is_sponsored = 3,
         ads_before_5th_fyp = 4,
         video_theme = 5,
         video_format = 6,
         has_captions = 7,
         has_hashtags = 8,
         like_count = 9,
         share_count = 10,
         comment_count = 11)
```


```{r,fig.height=5, fig.width = 12}
themes_by_duration <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = factor(video_duration, 
                           levels = c("Under 15 sec", "15-29 sec", "30-59 sec", 
                                      "1-3 min", "Over 3 min")), 
               fill = video_theme)) +
  labs(title = "Shorter Videos, Bigger Impact?",
       subtitle = "Exploring TikTok Video Themes and Duration",
       caption = "Source: TikTok FYP Content Analysis (Self-Collected Data)",
       x = "Video Duration",
       y = "Count")
themes_by_duration

```

```{r,fig.height=5, fig.width = 12}
duration_bar_chart <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = factor(video_duration, 
                           levels = c("Under 15 sec", "15-29 sec", "30-59 sec", 
                                      "1-3 min", "Over 3 min"))), 
           fill = "#3a7ca5") +
  labs(title = "The Duration Debate: Short vs Long",
       subtitle = "Exploring the Distribution of Video Lengths on TikTok's For You Page (FYP)",
       caption = "Source: TikTok FYP Content Analysis (Self-Collected Data)",
       x = "Video Duration",
       y = "Count")
duration_bar_chart
```


## TikTok FYP Performance Snapshot
Live monitoring of ad thresholds and content engagement


```{r}
# The maximum number of ads before 5th FYP to understand the highest ad count.
ads_before_5th_fyp <- latest_data$ads_before_5th_fyp
ads_max <- max(ads_before_5th_fyp, na.rm = TRUE)

# The mean number of ads before the 5th FYP to understand the typical ad exposure in the data
ads_mean <- mean(ads_before_5th_fyp, na.rm = TRUE)

# The average comment count to understand general engagement across videos.
comment_count <- latest_data$comment_count
comment_count_mean <- mean(comment_count,na.rm = TRUE)

like_count_max <- max(latest_data$like_count, na.rm = TRUE)

paste("The maximum number of ads before the 5th For You Page (FYP) is: ", ads_max)
paste0("The maximum like count across all videos is: ", like_count_max) 
```

The mean number of ads before the fifth For You Page (FYP) video is `r round(ads_mean, 2)` and the average comment count across videos is `r round(comment_count_mean, 2)` .
